Effects of Antenna Beam Chromaticity on Redshifted 21~cm Power Spectrum and Implications for Hydrogen Epoch of Reionization Array

### 2016-03-05 ForegroundSimulations/ms.tex
Update title, authors list, affiliations, keywords
From f2cbdf8 (fgsim):
====================

In ms.tex,

(*) Update title, authors list, affiliations and keywords

\shorttitle{Effects of Beam Chromaticity in EoR Power Spectra Measurements}
\shortauthors{Thyagarajan et~al.}

\def\ASU{\altaffilmark{1}}
\def\ASUtxt{\altaffiltext{1}{Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}}

\def\myemail{\altaffilmark{*}}
\def\myemailtxt{\altaffiltext{*}{e-mail: t\_nithyanandan@asu.edu}}

\def\UW{\altaffilmark{2}}
\def\UWtxt{\altaffiltext{2}{University of Washington, Department of Physics, Seattle, WA 98195, USA}}

\def\SKASA{\altaffilmark{3}}
\def\SKASAtxt{\altaffiltext{3}{Square Kilometre Array South Africa (SKA SA), Park Road, Pinelands 7405, South Africa}}

\def\RU{\altaffilmark{4}}
\def\RUtxt{\altaffiltext{4}{Department of Physics and Electronics, Rhodes University, Grahamstown 6140, South Africa}}

\def\CfA{\altaffilmark{5}}
\def\CfAtxt{\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}}

\def\ANU{\altaffilmark{6}}
\def\ANUtxt{\altaffiltext{6}{Australian National University, Research School of Astronomy and Astrophysics, Canberra, ACT 2611, Australia}}

\def\CAASTRO{\altaffilmark{7}}
\def\CAASTROtxt{\altaffiltext{7}{ARC Centre of Excellence for All-sky Astrophysics (CAASTRO)}}

\def\Haystack{\altaffilmark{8}}
\def\Haystacktxt{\altaffiltext{8}{MIT Haystack Observatory, Westford, MA 01886, USA}}

\def\MIT{\altaffilmark{9}}
\def\MITtxt{\altaffiltext{9}{MIT Kavli Institute for Astrophysics and Space Research, Cambridge, MA 02139, USA}}

\def\Curtin{\altaffilmark{10}}
\def\Curtintxt{\altaffiltext{10}{International Centre for Radio Astronomy Research, Curtin University, Perth, WA 6845, Australia}}

\def\Victoria{\altaffilmark{11}}
\def\Victoriatxt{\altaffiltext{11}{Victoria University of Wellington, School of Chemical \& Physical Sciences, Wellington 6140, New Zealand}}

\def\UWisc{\altaffilmark{12}}
\def\UWisctxt{\altaffiltext{12}{University of Wisconsin--Milwaukee, Department of Physics, Milwaukee, WI 53201, USA}}

\def\UMichigan{\altaffilmark{13}}
\def\UMichigantxt{\altaffiltext{13}{University of Michigan, Department of Atmospheric, Oceanic and Space Sciences, Ann Arbor, MI 48109, USA}}

\def\UMelbourne{\altaffilmark{14}}
\def\UMelbournetxt{\altaffiltext{14}{The University of Melbourne, School of Physics, Parkville, VIC 3010, Australia}}

\def\USydney{\altaffilmark{15}}
\def\USydneytxt{\altaffiltext{15}{The University of Sydney, Sydney Institute for Astronomy, School of Physics, NSW 2006, Australia}}

\def\CASS{\altaffilmark{16}}
\def\CASStxt{\altaffiltext{16}{CSIRO Astronomy and Space Science (CASS), PO Box 76, Epping, NSW 1710, Australia}}

\def\Tata{\altaffilmark{17}}
\def\Tatatxt{\altaffiltext{17}{National Centre for Radio Astrophysics, Tata Institute for Fundamental Research, Pune 411007, India}}

\def\RRI{\altaffilmark{18}}
\def\RRItxt{\altaffiltext{18}{Raman Research Institute, Bangalore 560080, India}}

\def\NRAO{\altaffilmark{19}}
\def\NRAOtxt{\altaffiltext{19}{National Radio Astronomy Observatory, Charlottesville and Greenbank, USA}}

\def\UWA{\altaffilmark{20}}
\def\UWAtxt{\altaffiltext{20}{International Centre for Radio Astronomy Research, University of Western Australia, Crawley, WA 6009, Australia}}

@@

\title{Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra}

@@

%% Author list
\author{
%% Lead Authors
Nithyanandan~Thyagarajan\ASU\myemail,
TBD
% Daniel~C.~Jacobs\ASU,
% Judd~D.~Bowman\ASU,
% N.~Barry\UW,
% A.~P.~Beardsley\UW,
% G.~Bernardi\SKASA$^,$\RU$^,$\CfA,
% F.~Briggs\ANU$^,$\CAASTRO,
% R.~J.~Cappallo\Haystack, 
% P.~Carroll\UW,
% B.~E.~Corey\Haystack, 
% % A.~A.~Deshpande\RRI, 
% A.~de~Oliveira-Costa\MIT,
% Joshua~S.~Dillon\MIT,
% D.~Emrich\Curtin,
% % B.~M.~Gaensler\USydney$^,$\CAASTRO, 
% A.~Ewall-Wice\MIT,
% L.~Feng\MIT,
% R.~Goeke\MIT,
% L.~J.~Greenhill\CfA,
% B.~J.~Hazelton\UW, 
% J.~N.~Hewitt\MIT,
% N.~Hurley-Walker\Curtin,
% M.~Johnston-Hollitt\Victoria,
% D.~L.~Kaplan\UWisc, 
% J.~C.~Kasper\UMichigan$^,$\CfA, 
% Han-Seek Kim\UMelbourne$^,$\CAASTRO,
% P.~Kittiwisit\ASU,
% E.~Kratzenberg\Haystack, 
% E.~Lenc\USydney$^,$\CAASTRO,
% J.~Line\UMelbourne$^,$\CAASTRO,
% A.~Loeb\CfA,
% C.~J.~Lonsdale\Haystack, 
% M.~J.~Lynch\Curtin, 
% B.~McKinley\UMelbourne$^,$\CAASTRO,
% S.~R.~McWhirter\Haystack,
% D.~A.~Mitchell\CASS$^,$\CAASTRO, 
% M.~F.~Morales\UW, 
% E.~Morgan\MIT, 
% A.~R.~Neben\MIT,
% D.~Oberoi\Tata, 
% A.~R.~Offringa\ANU$^,$\CAASTRO, 
% S.~M.~Ord\Curtin$^,$\CAASTRO,
% Sourabh Paul\RRI,
% B.~Pindor\UMelbourne$^,$\CAASTRO,
% J.~C.~Pober\UW,
% T.~Prabu\RRI, 
% P.~Procopio\UMelbourne$^,$\CAASTRO,
% J.~Riding\UMelbourne$^,$\CAASTRO,
% A.~E.~E.~Rogers\Haystack, 
% A.~Roshi\NRAO, 
% N.~Udaya~Shankar\RRI, 
% Shiv~K.~Sethi\RRI,
% K.~S.~Srivani\RRI, 
% R.~Subrahmanyan\RRI$^,$\CAASTRO, 
% I.~S.~Sullivan\UW,
% M.~Tegmark\MIT,
% S.~J.~Tingay\Curtin$^,$\CAASTRO, 
% C.~M.~Trott\Curtin$^,$\CAASTRO,
% M.~Waterson\Curtin$^,$\ANU,
% R.~B.~Wayth\Curtin$^,$\CAASTRO, 
% R.~L.~Webster\UMelbourne$^,$\CAASTRO, 
% A.~R.~Whitney\Haystack, 
% A.~Williams\Curtin, 
% C.~L.~Williams\MIT,
% C.~Wu\UWA,
% J.~S.~B.~Wyithe\UMelbourne$^,$\CAASTRO
}

%Institutional footnotes (typeset, then rearrange here to be in order)
\ASUtxt
% \UWtxt
% \SKASAtxt
% \RUtxt
% \CfAtxt
% \ANUtxt
% \CAASTROtxt
% \Haystacktxt
% \MITtxt
% \Curtintxt
% \Victoriatxt
% \UWisctxt
% \UMichigantxt
% \UMelbournetxt
% \USydneytxt
% \CASStxt
% \Tatatxt
% \RRItxt
% \NRAOtxt
% \UWAtxt
\myemailtxt

@@

\keywords{cosmology: observations --- dark ages, reionization, first stars --- large-scale structure of universe --- methods: statistical --- radio continuum: galaxies --- techniques: interferometric}

@@

\subsection{EoR Model}\label{sec:EoR-model}

@@

It must be emphasized that such a significant spillover is not limited by the horizon limits of the {\it foreground wedge} because this is caused by spectral structure in the antenna beam pattern in addition to that caused by position-dependent geometric phase in the visibility spectra. As a result delay-based complex deconvolution techniques such as CLEAN \citep{tay99,par09,par12b} that rely on smoothness of foreground spectra and only spectral window shape will not have adequate information to accurately deconvolve intrinsic supra-horizon spillover arising from the chromaticity of the antenna beam. We leave delay power spectrum estimation using {\it foreground removal} strategy that accounts for direction-dependent and beam chromaticity-dependent effects to future work and use only simple {\it foreground avoidance} approach in this study.

>>>>

\shorttitle{Effects of Beam Chromaticity on EoR Power Spectra Measurements}
\shortauthors{Thyagarajan et~al.}

\def\ASU{\altaffilmark{1}}
\def\ASUtxt{\affil{\altaffilmark{1}Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}}

\def\UCB{\altaffilmark{2}}
\def\UCBtxt{\affil{\altaffilmark{2}Dept. of Astronomy, University of California, Berkeley, CA, USA}}

\def\MIT{\altaffilmark{3}}
\def\MITtxt{\affil{\altaffilmark{3}MIT Kavli Institute for Astrophysics and Space Research, Cambridge, MA 02139, USA}}

% \def\ASU{\altaffilmark{1}}
% \def\ASUtxt{\altaffiltext{1}{Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}}

% \def\UCB{\altaffilmark{2}}
% \def\UCBtxt{\altaffiltext{2}{Dept. of Astronomy, University of California, Berkeley, CA, USA}}

% \def\MIT{\altaffilmark{3}}
% \def\MITtxt{\altaffiltext{3}{MIT Kavli Institute for Astrophysics and Space Research, Cambridge, MA 02139, USA}}

\def\myemail{\altaffilmark{$\dagger$}}
\def\myemailtxt{\altaffiltext{$\dagger$}{e-mail: t\_nithyanandan@asu.edu}}

@@

\title{Effects of Antenna Beam Chromaticity on Redshifted 21~cm Power Spectrum and Implications for Hydrogen Epoch of Reionization Array}
% \title{Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra}

@@

%% Author list
\author{
%% Lead Authors
Nithyanandan~Thyagarajan\ASU\myemail,
Aaron~R.~Parsons\UCB,
David~R.~DeBoer\UCB,
Judd~D.~Bowman\ASU,
%% Co-authors
Nipanjana~Patra\UCB,
Aaron~M.~Ewall-Wice\MIT,
Abraham~R.~Neben\MIT
}

%Institutional footnotes (typeset, then rearrange here to be in order)
\ASUtxt
\UCBtxt
\MITtxt
\myemailtxt

@@

\keywords{cosmology: observations --- dark ages, reionization, first stars --- instrumentation: interferometers --- large-scale structure of universe --- radio continuum: galaxies --- techniques: interferometric}

@@

\subsection{EoR Models}\label{sec:EoR-model}

@@

It must be emphasized that such a significant spillover is not bound by the horizon limits of the {\it foreground wedge} because this is caused by spectral structure in the antenna beam pattern in addition to that caused by position-dependent geometric phase in the visibility spectra. As a result delay-based complex deconvolution techniques such as CLEAN \citep{tay99,par09,par12b} that rely on smoothness of foreground spectra and only spectral window shape will not have adequate information to accurately deconvolve intrinsic supra-horizon spillover arising from the chromaticity of the antenna beam. We leave delay power spectrum estimation using {\it foreground removal} strategy that accounts for direction-dependent and beam chromaticity-dependent effects to future work and use only simple {\it foreground avoidance} approach in this study.
